\toolname: Property-Based Testing for MPC Security

### 2023-11-03 paper/main.tex
example cho

\todo{refer to an example figure and/or an appendix.}

@@

>>>>

An example \langname program is provided in Appendix~\ref{sec:example-cho}.

@@

\section{Example \langname program}\label{sec:example-cho}

The following \langname uses oblivious-transfer based GMW to evaluate a circuit representing a "less than" function
between the two parties' inputs, interpreted as 2-bit binary numbers.
It is slightly shorter than the ones we used for our experiments;
to provide the closest possible comparison between different implementations in our experiments,
the \langname protocols we used included some "no-op" statements.

\begin{small}
\begin{verbatim}
-- two_bit_less_than.cho
MACRO secret_share(P1(x), P2()) AS
  s1 = FLIP @P1
  s2 = x + s1
  SEND s2 TO P2
ENDMACRO
MACRO and_gmw(P1(x2, y2), P2(x1, y1)) AS
  out2 = FLIP @P2
  g1_s2_00 = out2 + ((x1 + 0) ^ (y1 + 0))
  g1_s2_01 = out2 + ((x1 + 0) ^ (y1 + 1))
  g1_s2_10 = out2 + ((x1 + 1) ^ (y1 + 0))
  g1_s2_11 = out2 + ((x1 + 1) ^ (y1 + 1))
  out1 = OBLIVIOUSLY [[g1_s2_00,
                       g1_s2_01]?y2,
                      [g1_s2_10,
                       g1_s2_11]?y2
                     ]?x2 FOR P1
ENDMACRO
MACRO reveal(P1(x1), P2(x2)) AS
  SEND x1 TO P2
  SEND x2 TO P1
  y = x1 + x2
ENDMACRO
-- Read secrets
x0 = SECRET @P1
x1 = SECRET @P1
y2 = SECRET @P2
y3 = SECRET @P2
-- Set up shares
DO secret_share(P1(x0), P2()) GET(x0_1=s1,
                                  x0_2=s2)
DO secret_share(P1(x1), P2()) GET(x1_1=s1,
                                  x1_2=s2)
DO secret_share(P2(y2), P1()) GET(y2_1=s2,
                                  y2_2=s1)
DO secret_share(P2(y3), P1()) GET(y3_1=s2,
                                  y3_2=s1)
-- Circuit evaluation
g3_1 = ~y2_1
g3_2 = y2_2
DO and_gmw(P1(x0_1, g3_1), P2(x0_2, g3_2)
          ) GET(g4_1=out1, g4_2=out2)
g5_1 = ~x0_1
g5_2 = x0_2
DO and_gmw(P1(y2_1, g5_1), P2(y2_2, g5_2)
          ) GET(g6_1=out1, g6_2=out2)
g7_1 = ~y3_1
g7_2 = y3_2
g8_1 = ~g6_1
g8_2 = g6_2
DO and_gmw(P1(g7_1, g8_1), P2(g7_2, g8_2)
          ) GET(g9_1=out1, g9_2=out2)
DO and_gmw(P1(x1_1, g9_1), P2(x1_2, g9_2)
          ) GET(g10_1=out1, g10_2=out2)
DO and_gmw(P1(g4_1, g10_1), P2(g4_2, g10_2)
          ) GET(g11_1=out1, g11_2=out2)
g12_1 = g4_1 + g10_1
g12_2 = g4_2 + g10_2
g13_1 = g11_1 + g12_1
g13_2 = g11_2 + g12_2
-- Reveal output
DO reveal(P1(g13_1), P2(g13_2)) GET(r0=y)
OUTPUT r0
\end{verbatim}
\end{small}
